SI

### 2021-02-22 ms/si.Rmd
Fix mapping of colors in dry-down plot

# Define color-blind palette
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

# Set colors for desiccation intensity
salt_cols <- c("NaCl" = cbPalette[7], "MgNO3" = cbPalette[5], "LiCl" = cbPalette[6], "Control" = "white")

>>>>

# Set colors for desiccation intensity
salt_cols <- c(
  "NaCl" = cbPalette[["blue"]], 
  "MgNO3" = cbPalette[["yellow"]], 
  "LiCl" = cbPalette[["red"]], 
  "Control" = "white")
